### 2025-03-28 paper-aadm.tex
Add abstract
Update paper layout a little

Short abstract here (not more than 7 lines of text)

@@

% \vspace{1.5cc}
% \begin{section}
% {FILL SECTION TITLE HERE}
% \end{section}

\section{Introduction}

@@

\section{Main definitions}

@@

\section{Metagraphs}

@@

\section{On graphs with given girth.}

@@

\section{Solving systems of inequalities}

@@

\section{On selection of structure of metagraphs}

@@

\section{Conclusion.}

@@

\begin{table}[H]
\caption{This is a table caption. Tabels should be placed in the main text
near to the first time they are cited. Table caption should be above
the the table.}

\centering{}%
\begin{tabular}{|c|c|c|}
\hline 
type & A & B\tabularnewline
\hline 
\hline 
expression & $\frac{a}{b}$ & $a+b$\tabularnewline
\hline 
expression & $a\cdot b$ & $\int f\left(x\right){\rm d}x$\tabularnewline
\hline 
\end{tabular}
\end{table}

@@

%Fill the list of references in the alphabetical order here.
% Adopt the style like:

% \bibitem{bib1}
% {\small {\sc J. A. Baker:} {\it Isometries in normed spaces.}
% Amer. Math. Monthly, {\bf 78} (1971), 655--658.}

% \bibitem{bib2}
%  {\small {\sc A. Marshall, I. Olkin: }{\it Inequalities$:$ Theory of
% Majorization and Its Applications.} Academic Press, New York, 1979.}
% \end{thebibliography}

% \vspace{1cc}

% %Fill author(s) affiliation(s), address(es) and emails here:
% %example is shown
% \noindent
% {\bf John Doe}\\
% Department of Mathematics,\\
% University of Belgrade,\\
% Belgrade, Serbia\\
% E-mail: {\it joe.doe@mail.com}

% \vspace{0.1cc}

% \noindent
% {\bf Jane Doe}\\
% Department of Mathematics,\\
% University of Belgrade,\\
% Belgrade, Serbia\\
% E-mail: {\it jane.doe@mail.com}

% 1
\bibitem{zemor}
G. Zémor, On Expander Codes, IEEE Trans. on Information theory, IT-47
No 2, (2001) pp. 835–837.

% 2
\bibitem{johnson}
Johnson, Sarah. (2008). Introducing Low-Density Parity-Check Codes. 
% ~-- University of Newcastle, Australia, 2006.

% 3
\bibitem{gallager}
R. Gallager, "Low-density parity-check codes," in IRE Transactions on Information Theory, vol. 8, no. 1, pp. 21-28, January 1962, doi: 10.1109/TIT.1962.1057683

% 4
\bibitem{protographs}
J. Thorpe,
Low-density parity-check (LDPC) codes constructed from protographs.
~-- JPL, IPN Progress Rep., Aug. 2003, vol. 42–154.

% 5
\bibitem{skorohodov_reachability_problem}
Skorokhodov V.A. Generalization of the Reachability Problem on Directed Graphs
~-- Mathematics and Statistics, Vol. 8, No. 6, pp. 699 - 704, 2020. DOI: 10.13189/ms.2020.080610

% 6
\bibitem{tutte_graph_definition}
W.T. Tutte, Graph Theory. Cambridge University Press, Cambridge, 2001, 360 pp.
% https://books.google.rs/books?id=uTGhooU37h4C&printsec=frontcover#v=onepage&q&f=false

% 7
\bibitem{margulis_construction}
Margulis, G. A. (1982). Explicit constructions of graphs without short cycles and low density codes. Combinatorica, 2(1), 71–78. 
doi:10.1007/bf02579283
%% https://sci-hub.se/10.1007/bf02579283

% 9
%% Критика метода Маргулиса
\bibitem{margulis_critique}
David J.C. MacKay, Michael S. Postol, Weaknesses of Margulis and Ramanujan-Margulis Low-Density Parity-Check Codes, Electronic Notes in Theoretical Computer Science, Volume 74, 2003, Pages 97-104, ISSN 1571-0661, doi:10.1016/S1571-0661(04)80768-0.
% https://www.inference.org.uk/mackay/margulis.pdf

% 8
\bibitem{imrich_construction}
Imrich, W. (1984). Explicit construction of regular graphs without small cycles. Combinatorica, 4(1), 53–59. doi:10.1007/bf02579157 
%% https://sci-hub.se/10.1007/bf02579157

% 10
\bibitem{ldpc_encoding}
T. J. Richardson and R. L. Urbanke, "Efficient encoding of low-density parity-check codes," in IEEE Transactions on Information Theory, vol. 47, no. 2, pp. 638-656, Feb 2001, doi: 10.1109/18.910579

% 11
\bibitem{algebraic_aproach_to_sc_ldpc}
Beemer, A., Habib, S., Kelley, C. A., Kliewer, J. (2017). A generalized algebraic approach to optimizing SC-LDPC codes. In 55th Annual Allerton Conference on Communication, Control, and Computing, Allerton 2017 (pp. 672-679). (55th Annual Allerton Conference on Communication, Control, and Computing, Allerton 2017; Vol. 2018-January). Institute of Electrical and Electronics Engineers Inc. doi:10.1109/ALLERTON.2017.8262802

% https://web.njit.edu/~jkliewer/wp/paper/BHKK_Allerton17.pdf

% 12
\bibitem{lifts_of_graphs}
C. A. Kelley, "On codes designed via algebraic lifts of graphs," 2008 46th Annual Allerton Conference on Communication, Control, and Computing, Monticello, IL, USA, 2008, pp. 1254-1261, doi: 10.1109/ALLERTON.2008.4797704.

% https://typeset.io/pdf/on-codes-designed-via-algebraic-lifts-of-graphs-34h5sq5koc.pdf

% 13
\bibitem{vasic_combinatorial_construction}
B. Vasic and O. Milenkovic, "Combinatorial constructions of low-density parity-check codes for iterative decoding," in IEEE Transactions on Information Theory, vol. 50, no. 6, pp. 1156-1176, June 2004, doi: 10.1109/TIT.2004.828066.
% https://repository.arizona.edu/bitstream/handle/10150/641965/Combinatorial%20Constructions%20of%20Low-DensityParity-Check%20Codes%20for%20Iterative%20Decoding.pdf;jsessionid=9F016719B821C7D7CEBB9C48D7B37CB1?sequence=1

%14
\bibitem{Kim2002ExplicitCO}
Kim, Jon-Lark, Uri N. Peled, Irina G. Perepelitsa and Vera Pless. “Explicit Construction of Families of LDPC Codes with Girth at Least Six.” (2002).

>>>>

In this paper the problem of construction of regular bipartite graphs with great girth is considered. To solve this problem the special subset of graphs called metagraphs is introduced. Metagraph is a weighted graph for which an operation of expansion that depends on edge weights is specified. The required graph is one of the expansions of the metagraph. Theorems on correspondence between paths and cycles on metagraphs and their expansions are proved. To construct the required graphs the approach with finding of edge weights on metagraph by solving the system of inequalities constructed using the metagraph. The theorem on existence of a solution for any such system is proved. The tight upper bound of expansion graph girth is given. The algorithm that constructs bipartite graphs with any given girth is proposed.

@@

% \section{Introduction}
\vspace{1.5cc}
\begin{section}
{Introduction}

@@

\end{section}

% \section{Main definitions}

\vspace{1.5cc}
\begin{section}
{Main definitions}

@@

\end{section}

% \section{Metagraphs}

\vspace{1.5cc}
\begin{section}
{Metagraphs}

@@

\end{section}

% \section{On graphs with given girth.}

\vspace{1.5cc}
\begin{section}
{On graphs with given girth.}

@@

\end{section}

% \section{Solving systems of inequalities}

\vspace{1.5cc}
\begin{section}
{Solving systems of inequalities.}

@@

\end{section}

% \section{On selection of structure of metagraphs}

\vspace{1.5cc}
\begin{section}
{On selection of structure of metagraphs.}

@@

\end{section}

% \section{Conclusion}

\vspace{1.5cc}
\begin{section}
{Conclusion.}

@@

\end{section}

@@

%Fill the list of references in the alphabetical order here.

% 1\
\bibitem{zemor}
{\small {\sc G. Zémor:} {\it On Expander Codes.} IEEE Trans. on Information theory, IT-47 No 2, (2001), 835--837.}

% 2
\bibitem{johnson}
{\small {\sc Johnson, Sarah: }{\it Introducing Low-Density Parity-Check Codes.} 2008.}

% 3
\bibitem{gallager}
{\small {\sc R. Gallager:} {\it Low-density parity-check codes.} IRE Transactions on Information Theory, vol. 8, No. 1, (1962), 21--28, doi: 10.1109/TIT.1962.1057683}

% 4
\bibitem{protographs}
{\small {\sc J. Thorpe:} {\it Low-density parity-check (LDPC) codes constructed from protographs.} JPL, IPN Progress Rep. vol. 42–154, (Aug. 2003)}

% 5
\bibitem{skorohodov_reachability_problem}
 {\small {\sc Skorokhodov V.A.: }{\it Generalization of the Reachability Problem on Directed Graphs.} Mathematics and Statistics, Vol. 8, No. 6, pp. 699 - 704, 2020. DOI: 10.13189/ms.2020.080610.}

% 6
\bibitem{tutte_graph_definition}
{\small {\sc W.T. Tutte: }{\it Graph Theory.} Cambridge University Press, Cambridge, 2001, 360 pp.}
% https://books.google.rs/books?id=uTGhooU37h4C&printsec=frontcover#v=onepage&q&f=false

% 7
\bibitem{margulis_construction}
{\small {\sc Margulis, G. A.: }{\it Explicit constructions of graphs without short cycles and low density codes.} Combinatorica, 2(1), 71–78. (1982) doi:10.1007/bf02579283}
%% https://sci-hub.se/10.1007/bf02579283

% 8
%% Критика метода Маргулиса
\bibitem{margulis_critique}
{\small {\sc David J.C. MacKay, Michael S. Postol: }{\it Weaknesses of Margulis and Ramanujan-Margulis Low-Density Parity-Check Codes.} Electronic Notes in Theoretical Computer Science, Volume 74, 2003, Pages 97-104, ISSN 1571-0661, doi:10.1016/S1571-0661(04)80768-0}
% https://www.inference.org.uk/mackay/margulis.pdf

% 9
\bibitem{imrich_construction}
{\small {\sc Imrich, W.: }{\it Explicit construction of regular graphs without small cycles.} Combinatorica, 4(1), 53–59. (1984) doi:10.1007/bf02579157 } 
%% https://sci-hub.se/10.1007/bf02579157

% 10
\bibitem{ldpc_encoding}
{\small {\sc T. J. Richardson and R. L. Urbanke: }{\it Efficient encoding of low-density parity-check codes.} IEEE Transactions on Information Theory, vol. 47, no. 2, pp. 638-656, Feb 2001, doi: 10.1109/18.910579 }

% 11
\bibitem{algebraic_aproach_to_sc_ldpc}
{\small {\sc Beemer, A., Habib, S., Kelley, C. A., Kliewer, J.: }{\it A generalized algebraic approach to optimizing SC-LDPC codes.} In 55th Annual Allerton Conference on Communication, Control, and Computing, Allerton 2017 (pp. 672-679).Institute of Electrical and Electronics Engineers Inc. doi:10.1109/ALLERTON.2017.8262802 }
% https://web.njit.edu/~jkliewer/wp/paper/BHKK_Allerton17.pdf

% 12
\bibitem{lifts_of_graphs}
{\small {\sc C. A. Kelley: }{\it On codes designed via algebraic lifts of graphs.} 2008 46th Annual Allerton Conference on Communication, Control, and Computing, Monticello, IL, USA, 2008, pp. 1254-1261, doi: 10.1109/ALLERTON.2008.4797704.}
% https://typeset.io/pdf/on-codes-designed-via-algebraic-lifts-of-graphs-34h5sq5koc.pdf

% 13
\bibitem{vasic_combinatorial_construction}

{\small {\sc B. Vasic and O. Milenkovic: }{\it Combinatorial constructions of low-density parity-check codes for iterative decoding.} in IEEE Transactions on Information Theory, vol. 50, no. 6, pp. 1156-1176, June 2004, doi: 10.1109/TIT.2004.828066. }
% https://repository.arizona.edu/bitstream/handle/10150/641965/Combinatorial%20Constructions%20of%20Low-DensityParity-Check%20Codes%20for%20Iterative%20Decoding.pdf;jsessionid=9F016719B821C7D7CEBB9C48D7B37CB1?sequence=1

%14
\bibitem{Kim2002ExplicitCO}
{\small {\sc Kim, Jon-Lark, Uri N. Peled, Irina G. Perepelitsa and Vera Pless: }{\it “Explicit Construction of Families of LDPC Codes with Girth at Least Six.} Proceedings of the 40th Allerton Conference on Communication, Control and  Computing, UIUC, Oct. 2002}
